\documentclass{beamer}

\ifx\themename\undefined
  \def\themename{Berlin}
\fi

\usetheme{\themename}

\beamertemplatetransparentcovered

\usepackage{times}
\usepackage[T1]{fontenc}

\title{A quick intro to \LaTeX}
\subtitle{These slides are made using \LaTeX\
		and I'll show you the source later :)}

\author{Felix Farquharson}
\institute{Group Project\\ CS2SOMETHING}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Outline}
  \tableofcontents
\end{frame}

\section{What is \LaTeX{} then?}
\subsection{Removing the design from the data...}

\begin{frame}<1>
  \frametitle{Good practice?}

  \begin{block}{the theory}
    It is good structure to split the design from the content because they 
	are two seperate things.
  \end{block}

\
\

\LaTeX{} is a typesetting program, you heard about it brefly in CS101
last year. It helps to ensure a document is consistant.

\end{frame}

\subsection{Why it's better.}

\begin{frame}<2>
\frametitle{But why is this better?}

\begin{itemize}
\item \LaTeX{} allows us to define just the information as it is relavant.
\item In some cases the design is part of the information. \LaTeX{}
allows us some control over the look and feel of the information.
But it makes sure everything is consistent and keeps references
up to date for us.
\item it allows easier version controll in our situation,
because it is based on text files.
\end{itemize}
\end{frame}

\begin{frame}<3>
\frametitle{\emph{Is} this better?}

\begin{block}{Questions?}
Are there any questions on why we would want to use \LaTeX{} before we
move on to how to use it?
\end{block}
\end{frame}

\section{And how?}
\subsection{Intro to commands.}

\begin{frame}<4>[fragile, plain]
\frametitle{how do i use it?}

\begin{block}{example document}
\begin{verbatim}\documentclass[12pt]{article}	
	^^ set the class (article is basic)
\begin{document}	<< begin the code for 
			   the document
\title{sample doc}	<< sets the title
\maketitle		<< makes a title page
\section{introduction}
\subsection{first}
This			<< ignores the whitespace
is the first part.\\	<< explicit newline.
This is the second line.
\end{document}		<< end the document
\end{verbatim}
\end{block}

\end{frame}

\subsection{Resources}

\begin{frame}<5>[fragile]
\frametitle{Useful resources}

\begin{verbatim}
http://www.maths.tcd.ie/~dwilkins/LaTeXPrimer/

http://www.uncg.edu/cmp/reu/presentations/
	Charles%20Batts%20-%20Beamer%20Tutorial.pdf
\end{verbatim}
\
\
I couldn't find the template, please let me know if you find it.
\end{frame}
\end{document}
