\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fullpage}
\begin{document}
\section{Personal Reflection}
\subsection{Name:}
Ben Brooks
\subsection{User name:}
beb12
\subsection{Group Number:}
06
\subsection{Role within the group:}
QA Manager/Coder
\subsection{Reflection}
During this project, as QA manager, I was responsible for ensuring consistent and high quality work produced by the group. This involved reading through all of the QA documents, understanding what the group had to do and also reviewing code, documentation and any other things the group produced. I feel as though overall the group has put in a decent amount of effort and as a result have produced a reasonable attempt at completing the objective of the assignment. We hit a few pretty major snags on the way, which impacted on the overall final result, however I do believe what we did get done was up to a high standard and had we not hit those snags, we would've had a very good product at the end.\\
\\
Throughout the project I worked in small teams, usually between 2 and 3 people on things. This was mostly pair programming with James and Felix to integrate the GUI with the backend of the program. One of my main contributions to the coding side of the project was the GUI. Felix had set out a base using Twitter Bootstrap and I then enhanced it with modal dialogs, friend menus, and getting the GET/POST functionality working.\\
\\
I feel as though this project has given me a very good grasp on how to use Git as a version control system, as I had not used it before this however I feel very comfortable using it now.\\
\\
I believe that James has been a very good group leader, everything was always clear when instructions were given and very reasonable timeframes were set for work. Problems were quickly resolved and he was very approachable with any issues that people had.
\end{document}
